---
title: "HW_1_Rojas"
author: "Ekaterina"
date: "2/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##MSCI 599: Marince Science Data with R 
### Homework 1 - Things my dog Maia ate in the last two weeks 

```{r}
maia <- read.csv("data/hw1_Maia_things_she_ate.csv", header = TRUE, sep= ",")
```

This a list of things that my dog Maia ate in the past few weeks. I chose to collect these data because this is part of my life now as a human mom for a crazy 7-month puppy who thinks that all the things in the world are meant to be chewed. 

*** 

I calculated a quantitative and qualitative severity level of the things she ate based on my reaction and the outcome, consequences of the event. 

Here the results: 

``` {r}

print(maia)
```

And here the mean of the quantitative severity level of the things she ate: 

```{r}

mean(maia$Quantitative.Severity.level)
```
Thus, the mean severity level for things that Maia ate are higher than 5. Which probably implies that she is a crazy puppy. 

